Title

### 2013-03-28 TCAD2013/overclocking_tcad.tex
Add Figures for CSA section

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/tex-archive/info/epslatex/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

@@

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/

@@

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Do not use the stfloats baselinefloat ability as IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/dblfloatfix/

@@

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
\title{Bare Demo of IEEEtran.cls for Journals}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{Michael~Shell,~\IEEEmembership{Member,~IEEE,}
        John~Doe,~\IEEEmembership{Fellow,~OSA,}
        and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
\thanks{M. Shell is with the Department
of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
\thanks{Manuscript received April 19, 2005; revised December 27, 2012.}}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
The abstract goes here.
\end{abstract}

@@

\subsection{Timing Models for $n$-bit Carry Selct Adder}
In this section, we describe the modeling method for the CSA timing, with the aim of forming the relationship between the operating frequency and the corresponding maximum word-length of CSA. This information can be employed to determine the truncation error based on the models presented in Section.xxx.

In an $n$-stage CSA, let the stage delay be denoted as $d_{0}\dots d_{n-1}$, where $d_{0}$ and $d_{n-1}$ represent the delay of MSB stage and LSB stage, respectively. In our analysis, we follow the previous assumption that delay is caused due to carry propagation and, in this case, multiplexing. Thus the delay of the $i^{th}$ stage can be obtained through~(\ref{CSA_SingleStageDelay}), where $\mu_{carry}$ denotes the delay of $1$-bit carry propagation and $\mu_{mux}$ detnoes the delay of multiplexer.
\begin{eqnarray}\label{CSA_SingleStageDelay}
  d_i=n_i\cdot \mu_{c}+(i+1)\cdot\mu_{mux} 
 % d_0=n_0\cdot \mu_{carry}+\mu_{mux}
\end{eqnarray}

@@

Using this information, we verify our model with the results obtained through post place and route simulations of Xilinx Virtex-6 FPGA. Figure.xxx demonstrates both the modeled value and the experimental results of the maximum word-length of RCA and 2-stage CSA, respectively, under a given operating frequency. Note that tht maximum input word-length is 16-bit, hence the modeled value is set to 16 if it expires.

@@

\subsection{Area Overhead}
Figure.xxx demonstrates the maximum word-length for RCA and CSA with 2 stages and 3 stages respectively under a range of operating frequencies. We only investigate 3 stages since the maximum stages number predicted in (\ref{CSA_StageNumber}) is 3. It can be seen that in comparison to RCA, CSA achieves greater word-length when frequency is intially increased. This means smaller truncation error can be obtained by CSA for a given frequency. RCA outperforms than CSA when very high frequency is applied, which in turn leads to small word-length for both structures. In addition, the word-length of 3-stage CSA is always greater than 2-stage CSA across the entire frequency domain, as expected.

%CSA achieves greater word-length than RCA when frequency is initially increased

However, the accuracy benefits brought by CSA comes with the cost of large area overhead. Figure.xxx depicts the resource usage (in terms of the number of Look-Up Tables (LUTs)) used for all three structures. It can be seen that the 3-stage CSA consumes $2.4\times\sim3.7\times$ area than RCA, while the number of the 2-stage CSA is $1.7\times\sim3.1\times$.

the 3-stage CSA costs

The stage number is determined by (\ref{CSA_StageNumber})

@@

\appendices
\section{Proof of the First Zonklar Equation}
Appendix one text goes here.

% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
\section{}
Appendix two text goes here.

>>>>

% *** GRAPHICS RELATED PACKAGES ***
%
%\usepackage{graphicx}
\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  \graphicspath{{../Figures/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  \DeclareGraphicsExtensions{.eps}
\fi
\usepackage{epstopdf}
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/tex-archive/info/epslatex/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

@@

% *** SUBFIGURE PACKAGES ***
\usepackage[tight,footnotesize]{subfigure}
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/

@@

\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Do not use the stfloats baselinefloat ability as IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/dblfloatfix/

@@

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
\title{Title}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{Kan~Shi,
        David~Boland,~\IEEEmembership{Member,~IEEE,}
        and~George~A.~Constantinides,~\IEEEmembership{Senior~Memberellow,~IEEE}% <-this % stops a space
	\thanks{K. Shi, D. Boland and G. A. Constantinides are with the Department of Electrical and Electronic Engineering, Imperial College London, London, UK}%
	%\thanks{M. Shell is with the Department of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
%\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
\thanks{Manuscript received April 19, 2005; revised December 27, 2012.}}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
The abstract.
\end{abstract}

@@

\subsection{Timing Models for $n$-bit Carry Select Adder}
In this section, we describe the modelling method for the CSA timing, with the aim of forming the relationship between the operating frequency and the corresponding maximum word-length of CSA. This information can be employed to determine the truncation error based on the models presented in Section.xxx.

In an $n$-stage CSA, let the stage delay be denoted as $d_{0}\dots d_{n-1}$, where $d_{0}$ and $d_{n-1}$ represent the delay of MSB stage and LSB stage, respectively. In our analysis, we follow the previous assumption that delay is caused due to carry propagation and, in this case, multiplexing. Thus the delay of the $i^{th}$ stage can be obtained through~(\ref{CSA_SingleStageDelay}), where $\mu_{carry}$ denotes the delay of $1$-bit carry propagation and $\mu_{mux}$ denotes the delay of multiplexer.
\begin{eqnarray}\label{CSA_SingleStageDelay}
  d_i=n_i\cdot \mu_{c}+(i+1)\cdot\mu_{mux} 
 % d_0=n_0\cdot \mu_{carry}+\mu_{mux}
\end{eqnarray}

@@

Using this information, we verify our model with the results obtained through post place and route simulations of Xilinx Virtex-6 FPGA. Fig.~\ref{CSA Model Verification} demonstrates both the modelled value and the experimental results of the maximum word-length of RCA and 2-stage CSA, respectively, under a given operating frequency. Note that the maximum input word-length is 16-bit, hence the modelled value is set to 16 if it expires. 
\begin{figure}[htbp]
  \centering
  \includegraphics[width=3in]{./Figures/Model.eps}
  \caption{Model Verification.}
  \label{CSA Model Verification}
\end{figure}

@@

\subsection{Area Overhead}
Fig.~\ref{CSA3stage Timing} demonstrates the maximum word-length for RCA and CSA with 2 stages and 3 stages respectively under a range of operating frequencies. We only investigate 3 stages since the maximum stages number predicted in (\ref{CSA_StageNumber}) is 3. It can be seen that in comparison to RCA, CSA achieves greater word-length when frequency is initially increased. This means smaller truncation error can be obtained by CSA for a given frequency. RCA outperforms than CSA when very high frequency is applied, which in turn leads to small word-length for both structures. In addition, the word-length of 3-stage CSA is always greater than 2-stage CSA across the entire frequency domain, as expected.  
\begin{figure}[htbp]
  \centering
  \includegraphics[width=3.3in]{./Figures/CSA3stage_Timing.eps}
  \caption{Maximum word-length for RCA and CSA across a variety of frequencies.}
  \label{CSA3stage Timing}
\end{figure}
%CSA achieves greater word-length than RCA when frequency is initially increased

However, the accuracy benefits brought by CSA comes with the cost of large area overhead. Fig.~\ref{CSA3stage Area} depicts the resource usage (in terms of the number of Look-Up Tables (LUTs)) used for all three structures. It can be seen that the 3-stage CSA consumes $2.4\times\sim3.7\times$ area than RCA, while the number of the 2-stage CSA is $1.7\times\sim3.1\times$. 
\begin{figure}[htbp]
  \centering
  \includegraphics[width=3.3in]{./Figures/CSA3stage_Area.eps}
  \caption{Area overhead for RCA and CSA.}
  \label{CSA3stage Area}
\end{figure}
%the 3-stage CSA costs

\subsection{Exploring Trade-offs Between Accuracy, Performance and Area}
Although advanced architectures such as CSA inheritly offer better performance than the basic structure, this would generate a large area overhead. In the following experiments, the trade-offs between accuracy, performance as well as area are explored. If the available hardware resources are limited, the full word-length of both CSA and RCA might not be implemented. Therefore truncation errors would be generated. For instance, the number of available LUTs is set to 45, 35, 25 and 15 respectively. The corresponding error expectations of RCA and CSA are demonstrated in Fig.xxx. The optimal design method which achieves the minimum error expectation is labelled.
\begin{figure}[htbp]
	\centering
	\includegraphics[width=3.3in]{./Figures/Error_LUT45.eps}
	\caption{LUT=45}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=3.3in]{./Figures/Error_LUT35.eps}
	\caption{LUT=35}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=3.3in]{./Figures/Error_LUT25.eps}
	\caption{LUT=25}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=3.3in]{./Figures/Error_LUT15.eps}
	\caption{LUT=15}
\end{figure}

%\begin{figure*}[htbp]
%  \centering
%  \subfigure[LUTs=45]{
%  \begin{minipage}[c]{0.45\textwidth}
%    \centering
%    \includegraphics[width=2in]{./Figures/Error_LUT45.eps}
%  \end{minipage}%
%  }%
%  \subfigure[LUT=35]{
%  \begin{minipage}[c]{0.45\textwidth}
%    \centering
%    \includegraphics[width=2in]{./Figures/Error_LUT35.eps}
%  \end{minipage}
%  }
%  \subfigure[LUT=25]{
%  \begin{minipage}[c]{0.45\textwidth}
%    \centering
%    \includegraphics[width=2in]{./Figures/Error_LUT25.eps}
%  \end{minipage}
%  }%
%  \subfigure[LUT=15]{
%  \begin{minipage}[c]{0.45\textwidth}
%    \centering
%    \includegraphics[width=2in]{./Figures/Error_LUT15.eps}
%  \end{minipage}
%  }
%  \caption{Accuracy-performance trade-offs under fixed area constraints.}
%  \label{Fig Tradeoffs}
%\end{figure*}
%the maximum word-lengths of RCA and CSA under given area constraints are listed in Table.xxx

It can be seen that if area is not limited, CSA with higher stage numbers serve as the optimal design choice for most frequency values, as we discussed in Section.xxx. While overclocking the RCA achieves better accuracy at higher frequencies, d
%According to

@@

%\appendices
%\section{Proof of the First Zonklar Equation}
%Appendix one text goes here.

% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
%\section{}
%Appendix two text goes here.
